
\begin{sidewaystable*}
\vspace*{45\baselineskip}
\caption{Project Competencies}
\label{tab:competencies}
\begin{tabularx}{\linewidth}{|l|X|X|}
\hline
 && \\
 & \textbf{Core Competencies\footnote{Projects included all core competencies}} & \textbf{Advanced Competencies\footnote{Projects included 2 or more advanced competencies, at least one of which was technical. Projects with 4+ were recommended to more advanced students.}} \\
  && \\ \hline && \\
\textbf{1. Software} & A.                 Identifying and defining problems using debugging techniques. &  \\
\textbf{Development Process} & B.                  Online and peer research to discover existing solutions to a problem. &  \\
 & C.                  Experimentation; learning by doing. &  \\
 & D.                 Developing and evaluating a set of proposed solutions to a problem. &  \\
 & E.                  Verifying that a problem is solved. &  \\
 & F.                  Documenting a solution for others. &  \\
  && \\ \hline && \\
\textbf{2. Interpersonal} & A.                 Working collaboratively and productively in a team. & \textbullet\ Technical writing. \\
 & B.                  Individual task management in an agile workflow. &  \\
 & C.                  Managing change and uncertainty. &  \\
 && \\ \hline && \\
\textbf{3. Cross-Functional} & A.                 Requirements gathering. & \textbullet\ Systematic thinking and architecture design. \\
 & B.                  Technical speaking / presentations. & \textbullet\ Project management. \\
 &  & \textbullet\ Speaking with customers and incorporating feedback. \\
 &  & \textbullet\ Risk management. \\
 &  & \textbullet\ User interface design. \\
 &  & \textbullet\ Business needs analysis and/or business case justification. \\
  && \\ \hline && \\
\textbf{4. Technical} & A.                 Software and/or hardware architecture. & \textbullet\ User analytics and data-driven design \\
 & B.                  OOP and/or functional programming. & \textbullet\ Statistics and data analysis. \\
 & C.                  Testing and quality assurance methodologies. & \textbullet\ Discrete mathematics. \\
 & D.                 Creating/refactoring and documenting code in a reusable manner. & \textbullet\ Machine learning. \\
 & E.                  Setting up and using modern development environments. & \textbullet\ API architectures, tradeoffs, and design. \\
 &  & \textbullet\ Consuming APIs. \\
 &  & \textbullet\ Cloud deployment and/or system administration. \\
 &  & \textbullet\ Containers and/or orchestration. (e.g. Docker, Kubernetes) \\
 &  & \textbullet\ Event programming methodologies (e.g. Kafka) \\
 &  & \textbullet\ Evaluating and improving system performance. \\
 &  & \textbullet\ Algorithm design and development. \\
 &  & \textbullet\ Distributed systems. \\
 &  & \textbullet\ Data modeling. \\
 &  & \textbullet\ Database design and development. \\
  && \\ \hline
\end{tabularx}
\end{sidewaystable*}